r5r: rapid realistic routing on multimodal transport networks with R5 in R

### 2020-11-13 r-package/paper2020/paper2020.Rmd
update paper

Additionally, the Porto Alegre dataset includes a `.csv` file containing the spatial coordinates of some of the city's points of interest. A sample of the Porto Alegre dataset, which will be used in the examples of this paper, is presented below:

@@

```{r, message = FALSE}
# reshape data
plot_data <- melt(ttm_tw, measure = patterns("^travel_time_p"), variable = "percentile", value = "travel_time")
plot_data[, mediantt := median(travel_time), by=fromId]

ggplot(data=plot_data, aes(y = travel_time, x = reorder(fromId, mediantt))) +
  geom_point(alpha = 0.05, size = .7) +
  geom_line(aes(y=mediantt, group=toId), color='blue') +
  expand_limits(y = 120) +
  scale_y_continuous(breaks = c(0, 30, 60, 90, 120)) +
  theme_minimal() +
  theme(axis.title.x = element_blank(), 
        axis.text.x = element_blank(),
        axis.ticks = element_blank(),
        panel.border = element_rect(fill = NA, colour = "grey80", size=1)) +
  labs(title = "Travel time variation among percentiles, per OD pair",
       y = "Travel Time (min)")

@@

```{r, message = FALSE}
# load points of interests and set origin and destination
points <- fread(file.path(data_path, "poa_points_of_interest.csv"))
origins <- points[c(10, 14),]
destinations <- points[c(12, 15),]

# set restrictions
max_walk_dist <- Inf

dit <- detailed_itineraries(r5r_core,
                            origins = origins,
                            destinations = destinations,
                            mode = mode,
                            departure_datetime = departure_datetime,
                            max_walk_dist = max_walk_dist,
                            max_trip_duration = max_trip_duration,
                            shortest_path = FALSE,
                            verbose = FALSE)

@@

dit$facet_labels <- paste0(dit$fromId, " to\n", dit$toId)

ggplot() +
   geom_sf(data = street_net$edges, color = "gray85") +
   geom_sf(data = dit, aes(color = mode), size = 1) +
   facet_wrap(~ facet_labels, nrow = 1) +
   theme_minimal() + 
   theme(legend.position = "bottom", axis.text.x = element_text(angle = 30, hjust = 1))
```

>>>>

A sample of the Porto Alegre dataset, which will be used in the examples of this paper, is presented below:

@@

```{r, message = FALSE}
# reshape data
plot_data <- melt(ttm_tw, measure = patterns("^travel_time_p"), variable = "percentile", value = "travel_time")
plot_data[, mediantt := median(travel_time, na.rm=T), by=fromId]

ggplot(data=plot_data, aes(y = travel_time, x = reorder(fromId, mediantt))) +
  geom_point(alpha = 0.01, size = .7) +
  geom_line(aes(y=mediantt, group=toId), color="#FE9F45", size=1.5) +
  expand_limits(y = 120) +
  scale_y_continuous(breaks = c(0, 30, 60, 90, 120)) +
  theme_minimal() +
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        axis.title.x = element_blank(), 
        axis.text.x = element_blank(),
        axis.ticks = element_blank(),
        panel.border = element_rect(fill = NA, colour = "grey80", size=1)) +
  labs(title = "Travel time uncertainty per destination",
       y = "Travel Time (min)", x='Destinations')

@@

```{r, message = FALSE}
dit <- detailed_itineraries(r5r_core,
                            origins = points[612],# 793
                            destinations = central_bus_stn,
                            mode = mode,
                            departure_datetime = departure_datetime,
                            max_walk_dist = max_walk_dist,
                            max_trip_duration = max_trip_duration,
                            shortest_path = FALSE,
                            verbose = FALSE)

@@

dit$facet_labels <- paste0("Alternative #", dit$option)

ggplot() +
  geom_sf(data = street_net$edges, color = "gray85") +
  geom_sf(data = dit, aes(color = mode), size = 1) +
  facet_wrap(.~facet_labels) +
  theme_minimal() + 
  theme(legend.position = "bottom", axis.text.x = element_text(angle = 30, hjust = 1))
```
